\textbf{Political Instability and Financial Markets}

### 2017-08-26 doc/paper.tex
Added PDF to repository

@@

\section{Public Protests} \label{sec: Public Protests}
The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests. While the previous section showed that the resignations themselves had large effects on stock returns and volatility, it is not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets. Indeed, corporate investors in the 2011 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.

The most recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more. The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership. Examples of public discontent included demonstrations, marches, riots and non-violent civil disobedience, and labor strikes.

The start and end dates in \autoref{tab:protest-list} are the dates that protests began and leader's resigned respectively. Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'etat Events Handbook and Archigos Version 4.1. Additional Lexis Nexis searches were used to verify these descriptions. Start dates were determined through similar means.

Column (1) suggests that public protests have no effect on stock returns. However, this occurs because some political movements increase stock prices while others decrease them. As shown in column (2), the absolute value of stock returns are over 2\% higher during public protests. These estimates would be biased if protest dates are correlated with higher world or regional stock market indices. To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index. The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 2\% higher during public protests. Finally, column (4) shows that stock volatility is more than 1 percentage point higher during political movements.

>>>>

\subsubsection{Public Protests} \label{subsec: Public Protests}
The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests. While the previous section showed that the resignations themselves had large effects on stock returns, it is not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets. Indeed, corporate investors in the 2011 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.

A recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more. The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership. Examples of public discontent included demonstrations, marches, riots, non-violent civil disobedience, and labor strikes.

The start and end dates in \autoref{tab:protest-list} are the dates that protests began and leader's resigned respectively. Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'etat Events Handbook and Archigos Version 4.1. Additional Lexis Nexis searches were used to verify these descriptions.

Column (1) suggests that public protests have no effect on stock returns. However, this occurs because some political movements increase stock prices while others decrease them. As shown in column (2), the absolute value of stock returns are over 2\% higher during public protests. These estimates would be biased if protest dates are correlated with higher world or regional stock market indices. To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index. The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 2\% higher during public protests. Finally, column (4) shows that stock volatility is more than 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \autoref{subsec: Volatility}.}

@@
